Face Attractiveness and the Sense of Reality

### 2022-09-27 analysis.Rmd
update

```{r message=FALSE, warning=FALSE}
outliers <- c(
  # Very short duration for questionnaire in particular + low rating correlations
  "5eaef8702b68455d6e130595_ptsga",
  "5f0f0a2a8b2a480447f31b21_lqgpz",
  "611d03b822d4c8e041ea0c32_m0knb",
  # Prefered not answering to sexual orientation: further analysis impossible
  "60eb34f117838a34a29a69d3_rxv85"
)
outliers_partial <- c(
  "5dc3485219ca0326027ce91f_37ho9",
  "5c6414540821d30001046198_x9q7r",
  "60dd7b03f1e72d38230df476_9yh9n",
  "5962799cb752840001ca478b_jh4sl",
  "5f44c23fbf2ddb80bcdf0edc_dnbny",
  "5e80370d48b5f47170e30e5c_5w2gf"
)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_att <- dfsub |>
  select(Participant, starts_with("Att")) |>
  pivot_longer(-Participant) |>
  # mutate(name = str_remove(name, "Cor_")) |>
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  scale_color_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  see::theme_modern() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top"
  ) +
  labs(y = "Score", fill = "") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

@@

df <- df |>
  filter(!Participant %in% outliers)
```

@@

  # Significance
  sig1 <- data.frame(x = 0.5, 
                     y = y_real[c(11, 31), "Predicted"],
                     Sex = y_real[c(11, 31), "Sex"])
  param <- parameters::parameters(m_real, effects = "fixed", keep = var)
  sig1$p <- c(min(param[str_detect(param$Parameter, sig1$Sex[1]), "p"]), min(param[str_detect(param$Parameter, sig1$Sex[2]), "p"]))
  sig1$y <- sig1$y + ifelse(sig1$Sex == "Male", 0.03, -0.03)
  sig1$label <- ifelse(sig1$p > .05 & sig1$p < .099, format_p(sig1$p), format_p(sig1$p, stars_only = TRUE))

  sig2 <- data.frame(x = 0.5, 
                     y =  y_conf[c(11, 31, 51, 71), "Predicted"],
                     Sex = y_conf[c(11, 31, 51, 71), "Sex"],
                     Belief = y_conf[c(11, 31, 51, 71), "Belief"]) |> 
    arrange(Sex, Belief)
  param <- parameters::parameters(m_conf, effects = "fixed", keep = var) |> 
    arrange(Parameter)
  sig2$p <- c(min(param$p[c(1, 2)]), min(param$p[c(5, 6)]), min(param$p[c(3, 4)]), min(param$p[c(7, 8)]))
  sig2$y <- sig2$y + ifelse(sig2$Belief == "Real", 0.02, -0.02)
  sig2$label <- ifelse(sig2$p > .05 & sig2$p < .099, format_p(sig2$p), format_p(sig2$p, stars_only = TRUE))

@@

@@

parameters::parameters(m_real, effects="fixed") |> 
  display()

>>>>

```{r message=FALSE, warning=FALSE}
outliers <- c(
  # More than 2 attention check fails
  "611d03b822d4c8e041ea0c32_m0knb",
  "5f0f0a2a8b2a480447f31b21_lqgpz",
  # Very short duration for questionnaire + low rating correlations (< 0.1)
  "5eaef8702b68455d6e130595_ptsga",
  "61356174c090b0083f131e01_asm81",
  # Prefered not answering to sexual orientation: further analysis impossible
  "60eb34f117838a34a29a69d3_rxv85"
)
outliers_partial <- c(
  # 1 attention check failed
  "5dc3485219ca0326027ce91f_37ho9",
  "5c6414540821d30001046198_x9q7r",
  "60dd7b03f1e72d38230df476_9yh9n",
  "5962799cb752840001ca478b_jh4sl",
  "5f44c23fbf2ddb80bcdf0edc_dnbny",
  "5e80370d48b5f47170e30e5c_5w2gf"
)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.width=20, fig.height=20}
p_att <- dfsub |>
  select(Participant, starts_with("Att")) |>
  pivot_longer(-Participant) |>
  # mutate(name = str_remove(name, "Cor_")) |>
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  scale_color_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
  see::theme_modern() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top"
  ) +
  labs(y = "Score", fill = "") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

@@

df <- df |>
  filter(!Participant %in% c(outliers))
```

@@

  # Significance
  sig1 <- data.frame(x = 0.5, 
                     y = y_real[c(11, 31), "Predicted"],
                     Sex = y_real[c(11, 31), "Sex"])
  param <- parameters::parameters(m_real, effects = "fixed", keep = var)
  sig1$p <- c(min(param[str_detect(param$Parameter, sig1$Sex[1]), "p"]), min(param[str_detect(param$Parameter, sig1$Sex[2]), "p"]))
  sig1$y <- sig1$y + ifelse(sig1$Sex == "Male", -0.03, 0.03)
  sig1$label <- ifelse(sig1$p > .05 & sig1$p < .099, format_p(sig1$p), format_p(sig1$p, stars_only = TRUE))

  sig2 <- data.frame(x = 0.5, 
                     y =  y_conf[c(11, 31, 51, 71), "Predicted"],
                     Sex = y_conf[c(11, 31, 51, 71), "Sex"],
                     Belief = y_conf[c(11, 31, 51, 71), "Belief"]) |> 
    arrange(Sex, Belief)
  param <- parameters::parameters(m_conf, effects = "fixed", keep = var) |> 
    arrange(Parameter)
  sig2$p <- c(min(param$p[c(1, 2)]), min(param$p[c(5, 6)]), min(param$p[c(3, 4)]), min(param$p[c(7, 8)]))
  sig2$y <- sig2$y + ifelse(sig2$Belief == "Real", 0.03, -0.03)
  sig2$label <- ifelse(sig2$p > .05 & sig2$p < .099, format_p(sig2$p), format_p(sig2$p, stars_only = TRUE))

@@

```{r message=FALSE, warning=FALSE, cache=cache}
analyze_interindividual <- function(df, questionnaire = "IPIP6_") {
  param_real <- data.frame()
  param_conf <- data.frame()
  for(var in names(select(df, starts_with(questionnaire)))) {
    m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", var)), 
                               data=datawizard::standardise(df, select=var), family = "binomial")
    param_real <- rbind(param_real, parameters::parameters(m_real, effects="fixed")[2, ])

    m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief / ", var)),

                               data=datawizard::standardise(df, select=var), 
                             family = glmmTMB::beta_family())

    param_conf <- rbind(param_conf, parameters::parameters(m_conf, effects="fixed")[3:4, ])
  }

  param_real <- param_real |> 
    mutate(Parameter = str_remove(Parameter, questionnaire)) |> 
    select(-SE)
  param_conf <- param_conf |> 
    tidyr::separate("Parameter", into = c("Belief", "Dimension"), sep = ":") |> 
    mutate(Belief = str_remove(Belief, "Belief"),
           Dimension = str_remove(Dimension, questionnaire)) |> 
    select(-SE)
  list(param_real, param_conf)
}
```

@@

parameters::parameters(m_real, effects="fixed", exponentiate = TRUE) |> 
  display()
